Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-12 doc/PRF2022/PRF_main.tex
results done

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation and the inset shows $N_b=60$ particles configuration.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
 Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary condition of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
$\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

@@

Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run that forms multiple bilayers with a vesicle like structure.

In case (ii) with $b = 1$, the boundary condition is positive everywhere.
It takes the maximum value $3a$ on tail and the
minimum value $a$ on the head side. 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers also adhere to one another 
forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with multiple layers.
At equilibrium, the number of folds depends primarily on the number of particles.
In addition, the inset provides a 3-fold structure when there are 60 particles.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)). We observe that 
when the number of particles is fewer, there is only single alternating pattern in particle orientations. Larger number of particles results two different patterns as shown in the figure.

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.

\section{Measuring deformation}
We use the free energy $F$,
a Euclidean distance-based measure $d(t)$,
and a scalar order parameter $S_{2}(t)$ to measure
the deformation of particle configurations under background flows.

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F[u] = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See the Appendix section \ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

To measure positional order, we use a strain parameter 
\begin{equation}
\label{eq:SP}
E(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \|E_i\|
\end{equation}
where $E_i = \tfrac{1}{2}(F_i^TF_i - I)$ is a Green-Lagrange strain tensor and $F_i$
is an approximate deformation gradient at particle $i$; $\| \cdot \|$ is the Frobeneous norm.
The motivation for  \eqref{eq:SP} is that 
for relatively weak background flow strengths, the near-equilibrium particle
collections behave as a solid and $E(t)$ is close to zero.
More generally, the Green-Lagrange strain tensor $E_i$ 
can be used to encode the energy of elastic deformations from the reference (equilibrium)
to deformed configuration and $E(t)$ gives a sense of how significant these deformations
may be.  Lacking a map from the reference state, 
we approximate a deformation gradient $F_i$ using weighted least squares for the system 
\[
F_i(\aa_j(t) - \aa_i(t)) = \aa_j(0) - \aa_i(0),\quad j = 1,\dots, N_b  
\]
with weights $w_i = \exp(-\|\aa_j(t) - \aa_i(t)\|/4c)$ where $c$ is particle radius.

To study orientational order, we use the scalar order parameter 
\begin{equation}
  \label{eq:S2}
S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the
orientation of the largest eigenvalue eigenvector of 
$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
A value $S_2(t) = 1$ indicates a complete orientational
order where all particle directors lie on a common axis e.g.,
two parallel vectors with possibly opposite direction are ordered. 
A value far from 1 indicates disorder.

The measure $S_2$ is an inadequate for the bilayer and
multilamellar structures.  For example, the directors of a circular
bilayer vesicle are uniformly distributed along a circle, even though
there is a strong orientational order between neighboring particles.
To account for these latter cases, we use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. We use different colors to distinguish from boundary conditions.
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters. The results of the striated configuration depend on the initial geometrical setup.
  }
\end{figure}

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs. For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions. This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
Figure~\ref{fig:relax_energy}(b) 
measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
structures have similar trends in small and large systems. The aggregation for striated configurations may have one or more different pattern formations when the number of particles is varied.

@@

\section{Results}
\label{sec:results}

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientations and the inset shows $N_b=60$ particles configuration.
  The particles self-assemble into distinct configurations,
  depending on the boundary condition \eqref{eq:bc-type}.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle giving bilayer structures. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
  The insest in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
  as the main panels.}
\end{caption}
\end{figure}

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
$\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

@@

Figure~\ref{fig:relax}(a)shows the initial configurations with orientations of 198-particle and 60- particle cases,
respectively. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head (green),
and takes the maximum value $a$ on the
hydrophobic tail (red). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run.
Both cases form bilayers with multiple components.

In case (ii) with $b = 1$, the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. 
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
    The results of the striated configuration, however, depend on the initial geometrical setup.
  }
\end{figure}

\section{Measuring deformation}
We use the free energy $F$,
a strain parameter $E$, 
and two scalar order parameters $S_{2}$ and $\tilde S_2$ to measure
the deformation of particle configurations under background flows.

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See the Appendix section \ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of number of particles.

To measure positional order, we use a number,
which we call the strain parameter, 
\begin{equation}
\label{eq:SP}
E = \frac{1}{N_b} \sum_{i=1}^{N_b}
\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\|
\end{equation}
where $\mathsf{F}_i$ is an 
approximate deformation gradient at particle $i$.
The argument inside the Frobenius norm $\| \cdot \|$
is the Green-Lagrange strain tensor.
The motivation for  \eqref{eq:SP} is as follows.
For relatively weak background flow strengths, the near-equilibrium particle
configurations behave as an elastic solid.  There is a map $\ff(\xx,t)$
from the reference (equilibrium) configuration with $\ff(\aa_i(0),t) = \aa_i(t)$
for $i = 1,\dots,N_b$.  Using linear approximation,
\[
\aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
\approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
\]
To approximate
the deformation gradient $\nabla \ff(\aa_i(0),t)$
we solved the overdetermined system 
\[
\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j = 1,\dots, N_b  
\]
for $\mathsf{F}_i$ by weighted least squares. The weights  
$w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
ensure that nearby particles contribute the most to the linear approximation at $\aa_i$.

Finally, we use the scalar order parameter for orientational order:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the
orientation of the largest eigenvalue eigenvector of 
$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
A value $S_2(t) = 1$ indicates 
that all particle directors lie on a common axis e.g.,
two parallel vectors with possibly opposite direction are ordered. 
A value far from 1 indicates disorder.

We must modify $S_2$ to account for the bilayer and
multilamellar structures.  In these cases, the directors 
are more or less bilayer uniformly distributed along a circle, even though
there is orientational order between neighboring particles.
To account for local order, we instead use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

Figure~\ref{fig:relax_energy}(b) 
tracks the orientational order parameter $\tilde{S}_2$.
Both bilayer and multilamellar
structures show similar trends in the small and large particle number systems
(Figure \ref{fig:relax}(b) black curves, red curves respectively).
The multilamellar structures are highly ordered in all cases (Figure~\ref{fig:relax}(c))
whereas the bilayer structures
are disordered because they consist of several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).

The aggregation for striated configurations form more than one 
pattern when the number of particles is varied (Figure~\ref{fig:relax}(d)).
We observe that when the number of particles is fewer, there is only
a single alternating pattern in particle orientations where the directors
are more or less parallel and alternate directions between stria (Figure~\ref{fig:relax}(d), inset).
Larger number of particles results in two different patterns: the alternating sign pattern
as in the small particle number case (Figure~\ref{fig:relax}(d), 
top right rectangle) and one where the directors reflect across the lines parallel
to the stria and across the lines perpendicular to the stria (Figure~\ref{fig:relax}(d),
top middle rectangle).
As a result, there are different trends in orientational order
(Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).

In the Results section,
the equilibrium configurations for cases (i), (ii), and (iii)
(Figure~\ref{fig:relax}, insets) are
used as initial data in the
background flow simulations. 
For the bilayer case (i), we include an alternate initial condition 
consisting of a single, circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
    with shear flow rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
    The initial configuration is shown in inset of panel (a).
    The streamlines are plotted in the background.
    Panel (d) plots the free energies,
    panel (e) shows the orientational parameter $\tilde{S}_2$,
    and panel (f) shows positional parameter E.
}
\end{figure}

\section{Results}
\label{sec:results}
In this section, we subject the Janus particle structures to various background
flows.  The purpose of this study is to understand how self-assembled particles
respond to external fluid forcing.  We can then compare the results to guage
the effective properties of materials comprised of Janus particles as a function
of their amphiphilic properties.  
%%%
%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}

\subsection{Bilayer configurations in a shear flow}
To begin, we place the bilayer structure (Figure~\ref{fig:relax}(b), inset)
in the shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The general pattern consists of a rotating body.  The various bilayer components
detach and reattach throughout so that the boyd is continuously changing morphology.
The supplementary movies show that these bilayers merge and form a worm-like shape in higher 
shear flows.

In terms of deformations, 
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  Note that the free energy takes
the form of a line tension because the simulations are two-dimensional.

An interesting feature of the simulations is that the $\tilde S_2$ order parameter
is on the average increasing (Figure~\ref{fig:BC1_shear}(e)).  In the initial configuration,
the structure has three or four components.  Under the shear flow, the detachment and reattachment
results in an overall decrease in the number of components.  This suggests that
the shear flow perturbs the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}

Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).
Our previous paper \cite{Fu2022_JFM} studied
The vesicle in a shear flow undergoes the familiar tank-treading deformation (Figure~\ref{fig:Ves_shear} (a)--(c)),
and based on previous results (\cite{Fu2022_JFM}),
we investigate the cases $\dot\gamma=0.05, 0.066, 0.075$.

Unlike the multiples component case, 
the energies for the vesicle case show jumps from the baseline value $30$ kT/nm to 32 kT/nm
signaling the rupture of the vesicle into multiple components
(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
After this initial break, the energies are more or less constant.

For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
(Figure \ref{fig:Ves_shear}(e), solid curve).
Following rupture ($\dot\gamma= 0.066$ and $\dot \gamma= 0.075$),
there is greater variation in the order parameter $\tilde{S}_2$
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}(e), dashed curves).
The oscillations occur due to the orbit of the two bilayer components,
and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.

Like with multiple component bilayer case, positional order diverges when the components of the ruptured
vesicle separate and drift off in opposite directions (Figure \ref{fig:Ves_shear}(f), dashed curves).

%%%%%%%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the bilayer/vesicles configurations to a 
Taylor-Green (TG) background flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
 \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
         {\bf e}_x
         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
             {\bf e}_y\right).
\end{equation}
The TG flow is a confining flow consisting of a checkboard pattern
of cells with alternating circulation.  We control the flow by the
the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
The default parameter $l=2$ is used through this work.
%

There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
There is no significant change in the orientational order.  There is an initial increase in the
strain parameter due to component mixing, but the strains remains bounded since the particles
stay confined to within the neighbors of the central cell.

Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
In these cases, there is little change in the vesicle free energy and order (Figure~\ref{fig:ves_TG}(d)-(f))).
The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
suggesting that the vesicle has a critical TG flow strength in the interval $[0.15, 0.2]$ separating the
intact and ruptured end-states.

The vesicle shape is also tied to cell size $l$.  
Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
For the smallest cell size $l = 1$ tested, the vesicle is somewhat octogonal
and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
For the largest cell size $l = 4$,
the vesicle is rhomboid and surrounds a single cell.

In all cases, the vesicle tank-treads like in the shear flow case.
The direction of the tank-treading, however, varies with the cell
size (Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
this variation to the total rotational moment of the cells that the vesicle
passes through.

We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
by averaging the area/length for the inner and outer leaflets.  
As shown in Figure~\ref{fig:BTG_Scale}(e),
the relative area $A/A_0$ decreases during the simulations, with a rate
depending nonmonotonically on $l$.  
The relative length $L/L_0$, is constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
This implies that the vesicle behaves as an inextensible, permeable membrane.
In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
in the context of shear background flow.

%%%
\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear}
Multilamellar structure in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.1, 0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
       }
\end{figure}

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (case (ii)) and striated (case (iii))
boundary conditions, in both shear and TG background flow.  The results are
qualitatively similar and will be presented in tandem. 
For the multilamellar case, we place a 60-particle configuration (inset of Figure~\ref{fig:BC2_shear}(a))
in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
For the striated case, we also place a 60-particle configuration (inset of Figure~\ref{fig:BC3_shear}(a))
in shear and TG background flows.  However, somewhat larger rates are required to see appreciable
deformations for this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$
and $V_0=0.2, 0.25, 0.3$ respectively.

In terms of shear flow, the free energies are steady at the lowest shear flow
rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
The free energy of the striated configuration oscillates by $\pm 1$ kT/nm
due to square reference region deforming into a rhomboidal shapre under shear
flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
is present in for the multilamellar configuration since this shape is circularly
isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
At the lowest shear rates, there is, however, oscillation in the strains
of both configurations, 
while the order parameter $\tilde S_2$ is more less constant
(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
In summary, both multilallar and striated configurations behave as rigid bodies
under shear flow.
